Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-03 thesis/abstract.tex
update with ch4 finished

We expand upon these findings with a more careful study of how varying the energy and spatial location of a given enrichment event changes how its metal yields mix within the ISM. We play particular attention to events that could be associated with different channels of r-process enrichment (for example, neutron star - neutron star mergers vs. hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patters in low mass dwarf galaxies. \textbf{Note to self to revisit once this chapter is written...}

>>>>

We expand upon these findings with a more careful study of how varying the energy and spatial location of a given enrichment event changes how its metal yields mix within the ISM. We play particular attention to events that could be associated with different channels of r-process enrichment (for example, neutron star - neutron star mergers vs. hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patterns in low mass dwarf galaxies. We find that -- on average -- the injection energy of a given enrichment source and the galaxy's global SFR at the time of injection play the strongest roles in regulating the mixing and ejection behavior of metals. Lower energy events are retained at a greater fraction and are more inhomogeneously distributed than metals from more energetic sources. However, the behavior of any single source varies dramatically, particularly for the low energy enrichment events. We further characterize the
effect of radial position and local ISM density on the evolution of metals from single enrichment events.
